Cell Decomposition of Rank 2 Quiver Grassmannians

### 2017-04-25 Grassmannian_cells.tex
test
Proof of Lemma 4.1

\newcommand{\bfe}{\mathbf{e}}
\newcommand{\bff}{\mathbf{f}}
\newcommand{\bfg}{\mathbf{g}}
\newcommand{\tbfe}{{\tilde\bfe}}
\newcommand{\tbff}{{\tilde\bff}}
\newcommand{\tbfg}{{\tilde\bfg}}
\newcommand{\C}{\mathbb{C}}

\newcommand{\Rep}{\mathrm{Rep}}
\newcommand{\Gr}{\mathrm{Gr}}
\renewcommand{\AA}{\mathbb{A}}
\newcommand{\kk}{\Bbbk}
\newcommand{\ZZ}{\mathbb{Z}}
\newcommand{\Ext}{\operatorname{Ext}}
\newcommand{\Hom}{\operatorname{Hom}}
\newcommand{\ses}[3]{0\rightarrow #1\rightarrow #2\rightarrow#3\rightarrow 0}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Quiver Grassmannians of $\widetilde{K(n)}$}
\noindent 
Let $\tilde P_m$ be a fixed lift of $P_m$ to the universal cover $\widetilde{K(n)}$. Note that the group $W_Q$ acts naturally on $\widetilde{K(n)}_0$ via translation, i.e. $w.(q,w')=(q,ww')$. Up to this action a lift $\tilde P_m$ of $P_m$ is unique.
\begin{lemma}
  \label{le:preprojective lifts}
  There exist lifts $\tilde P_{m-1,i}$ for $1\le i\le n$ of $P_{m-1}$ to $\widetilde{K(n)}$ so that:
  \begin{enumerate}
    \item $\Hom_Q(P_{m-1},P_m)\cong\bigoplus_{i=1}^n \Hom_{\tilde Q}(\tilde P_{m-1,i},\tilde P_m)$, where each $\Hom_{\tilde Q}(\tilde P_{m-1,i},\tilde P_m)$ is one-dimensional;
    \item For any proper subset $\{i_1,\ldots,i_k\}\subset\{1,\ldots,n\}$, there exists a short exact sequence
      \[0\longrightarrow \tilde P_{m-1,i_1}\oplus\cdots\oplus\tilde P_{m-1,i_k}\longrightarrow\tilde P_m\longrightarrow \tilde P_m^{i_1,\ldots,i_k}\longrightarrow 0;\]
    \item The lifts $\tilde P_{m-1,i}$ are pairwise orthogonal. 
    \item All nontrivial proper subrepresentations of $\tilde P_m^{i_1,\ldots,i_k}$ are preprojective.
  \end{enumerate}
\end{lemma}
\begin{proof}
Most of the things should directly follow from \cite{gab}, the fact that $F_Q$ is a covering functor and the considerations of the last section.
\end{proof}

@@

\end{proof}
\begin{lemma}\label{quotient}
 Consider $\ses{\tilde P_m}{\tilde P_{m+1}^{(k)}}{\tilde P_{m+1}^{(k-1)}}$. If $U\subset \tilde P_m$ such that $\Ext(\tilde P_{m+1}^{(k-1)},U)\neq 0$, then we have $\Ext(\tilde P_{m+1}^{(k-1)},\tilde P_m/U)= 0$.
\end{lemma}
\begin{proof}
Every $U\subset \tilde P_m$ gives rise to a commutative diagram
  \[\xymatrix{0\ar[r] &\tilde P_{m-1}^{n-1}\oplus \tilde P_{m-2}^{n-k}\ar[r] &  \tilde P_m\ar[r] & \tau\tilde P_{m+1}^{(k-1)}\ar[r] & 0 \\
  0\ar[r]& V\ar[r]\ar[u] & U\ar[u]\ar[r]& W\ar[r]\ar[u]& 0}\]

>>>>

\newcommand{\bfe}{\mathbf{e}}
\newcommand{\bff}{\mathbf{f}}
\newcommand{\bfg}{\mathbf{g}}
\newcommand{\tbfe}{{\tilde\bfe}}
\newcommand{\tbff}{{\tilde\bff}}
\newcommand{\tbfg}{{\tilde\bfg}}
\newcommand{\C}{\mathbb{C}}
\newcommand{\ui}{\underline i}
\newcommand{\uj}{\underline j}
\newcommand\udim{{\underline{\dim}\, }}

\newcommand{\Rep}{\mathrm{Rep}}
\newcommand{\Gr}{\mathrm{Gr}}
\renewcommand{\AA}{\mathbb{A}}
\newcommand{\kk}{\Bbbk}
\newcommand{\ZZ}{\mathbb{Z}}
\newcommand{\Ext}{\operatorname{Ext}}
\newcommand{\Hom}{\operatorname{Hom}}
\newcommand{\ses}[3]{0\rightarrow #1\rightarrow #2\rightarrow#3\rightarrow 0}
\newcommand{\Sc}[2]{\langle #1,#2\rangle}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Quiver Grassmannians of $\widetilde{K(n)}$}
\noindent 
Let $\tilde P_m$ be a fixed lift of $P_m$ to the universal cover $\widetilde{K(n)}$. Note that the group $W_Q$ acts naturally on $\widetilde{K(n)}_0$ via translation, i.e. $w.(q,w')=(q,ww')$. Up to this action a lift $\tilde P_m$ of $P_m$ is unique. On the universal covering, every preprojective representation $\tilde P_m$ has $n$ subrepresentation $\tilde P_{m-1,1},\ldots,\tilde P_{m-1,n}$. Each of them corresponds (inductively) to one of the $n$ different arrows of $K(n)$. In turn, with every sequence of natural numbers $\uj=(j_1,\ldots,j_k)$ with $j_i\leq n$ and $k\leq m-1$ we can associate a preprojective subrepresentation $\tilde P_{m-k,\uj}$ of dimension $(u_{m-k-1},u_{m-k})$. For $\{i_1,\ldots,i_k\}\subset \{1,\ldots,n\}$ and $k\leq n-1$, there exist exact sequences of the form
\[\ses{\bigoplus_{j=1}^k\tilde P_{m-1,i_j}}{\tilde P_m}{\tilde P_{m}^{(i_1,\ldots,i_k)}},\quad\quad\ses{\tilde P_{m-1,i_k}}{\tilde P_{m}^{(i_1,\ldots,i_{k-1})}}{\tilde P_{m}^{(i_1,\ldots,i_k)}}.\]

Using this notation, we obtain the following lemma:
\begin{lemma}
  \label{le:preprojective lifts}
  \begin{enumerate}
    \item $\Hom_Q(P_{m-1},P_m)\cong\bigoplus_{i=1}^n \Hom_{\tilde Q}(\tilde P_{m-1,i},\tilde P_m)$, where each $\Hom_{\tilde Q}(\tilde P_{m-1,i},\tilde P_m)$ is one-dimensional;
   % \item For any proper subset $\{i_1,\ldots,i_k\}\subset\{1,\ldots,n\}$, there exists a short exact sequence
   %   \[0\longrightarrow \tilde P_{m-1,i_1}\oplus\cdots\oplus\tilde P_{m-1,i_k}\longrightarrow\tilde P_m\longrightarrow \tilde P_m^{i_1,\ldots,i_k}\longrightarrow 0;\]
    \item The representations $\tilde P_{m-1,i}$ are pairwise orthogonal. 
    \item All nontrivial proper subrepresentations of $\tilde P_m^{(i_1,\ldots,i_k)}$ are preprojective.
  \end{enumerate}
\end{lemma}
\begin{proof}
The first statement should directly follow from \cite{gab} and the fact that $F_Q$ is a covering functor (precise reference). The second part follows for instance recursively by applying BGP-reflections.

For the third part, we proceed by induction. Clearly $\tilde P_m$ has only preprojective subrepresentations. We can assume without loss of generality that the subrepresentation $U$ is indecomposable. If $U\subsetneq P_m^{(i_1,\ldots,i_k)}$ were not preprojective, the embedding would not factor through $P_m^{(i_1,\ldots,i_{k-1})}$ by induction hypothesis.  Thus we get a commutative diagram

\[\xymatrix{0\ar[r] &\tilde P_{m-1,i_k}\ar[r] &  \tilde P_{m}^{(i_1,\ldots,i_k)}\ar[r] & \tilde P_{m}^{(i_1,\ldots,i_{k-1})}\ar[r] & 0 \\
  0\ar[r]&\tilde P_{m-1,i_k} \ar[r]\ar[u] & U'\ar[u]\ar[r]& U\ar[r]\ar[u]& 0}\]
where the vertical maps are injective. Then we have $U\in\tilde P_{m-1,i_k}^\perp$
because $$\Hom(\tilde P_{m-1,i_k},U)=\Hom(\tilde P_{m-1,i_k},\tilde P_{m}^{(i_1,\ldots,i_{k-1})})=0$$ and $\tilde P_{m-1,i_k}$ is preprojective and $U$ is not. Moreover, we have $\Hom(U,\tilde P_{m-1,i_k})=0$ for the same reason. Thus $U'$ is an indecomposable subrepresentation of $\tilde P_{m}^{(i_1,\ldots,i_{k})}$ (reference) such that
\[\Sc{\udim U'}{\udim U'}=\Sc{\udim U}{\udim U}+\Sc{\udim \tilde P_{m-1,i_k} }{\udim \tilde P_{m-1,i_k} }+\Sc{\udim U}{\tilde P_{m-1,i_k}}=1+\Sc{\udim U}{\tilde P_{m-1,i_k}}\leq 0\]
because we have $\Ext(U,\tilde P_{m-1,i_k})\neq 0$ as the bottom does not split.
But this contradicts the induction hypothesis because preprojective representations do not have self-extensions.

@@

\end{proof}
\begin{lemma}\label{quotient}
 Consider the non-split short exact sequence $\ses{\tilde P_m}{\tilde P_{m+1}^{(k)}}{\tilde P_{m+1}^{(k-1)}}$. If $U\subset \tilde P_m$ such that $\Ext(\tilde P_{m+1}^{(k-1)},U)\neq 0$, then we have $\Ext(\tilde P_{m+1}^{(k-1)},\tilde P_m/U)= 0$ or the fiber $\Psi^{-1}(U,\tilde P_{m+1}^{(k-1)})$ is empty.
\end{lemma}
\begin{proof}
Every $U\subset \tilde P_m$ gives rise to a commutative diagram
  \[\xymatrix{0\ar[r] &\tilde P_{m-1}^{n-1}\oplus \tilde P_{m-2}^{n-k}\ar[r] &  \tilde P_m\ar[r] & \tau\tilde P_{m+1}^{(k-1)}\ar[r] & 0 \\
  0\ar[r]& V\ar[r]\ar[u] & U\ar[u]\ar[r]& W\ar[r]\ar[u]& 0}\]
